---
title: "Lab1"
author: "Abinash Borah"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Creating a package in R
A package is a  fundamental unit of reproducible R code which include reusable R functions along with their documentation and sample data. 

Documentation about package making in R can be found at <https://r-pkgs.org/>

## About this exercise
In this Lab1 exercise, I have created an R package "Lab1Intro" that contains three functions to create from a data array X:

1. the sample mean vector : mean_vector(X)
1. the sample (biased) covariance matrix : covariance_matrix(X) 
1. the sample correlation matrix : correlation_matrix(X)

My package is available at the github repository <https://github.com/abinashborah/Lab1Intro>

## Following formulae are used in calculating the above quantities:

$$\overline{x}_k = \frac{1}{n}\sum_{j=1}^{n} x_{jk}\hspace{1cm}k = 1, 2,...,p$$


$${s}_{ik} = \frac{1}{n}\sum_{j=1}^{n} (x_{ji}-\overline{x}_i)(x_{jk}-\overline{x}_k)
\hspace{1cm}i = 1, 2,...,p,\hspace{0.5cm}k = 1, 2,...,p$$


$${r}_{ik} = \frac{{s}_{ik}}{{\sqrt{{s}_{ii}}}{\sqrt{{s}_{kk}}}} = \frac{\sum_{j=1}^{n} (x_{ji}-\overline{x}_i)(x_{jk}-\overline{x}_k)}
{\sqrt{\sum_{j=1}^{n}(x_{ji}-\overline{x}_i)^2}\sqrt{\sum_{j=1}^{n}(x_{jk}-\overline{x}_k)^2}}
\hspace{1cm}i = 1, 2,...,p,\hspace{0.5cm}k = 1, 2,...,p$$


$$\textbf{S} = \frac{1}{n-1}\textbf{X}^/\left(\textbf{I} - \frac{1}{n}\textbf{11}^/\right)\textbf{X}$$

\usepackage{amsmath}

$$\textbf{D}^{1/2} = \begin{bmatrix}
\sqrt{s_{11}} & 0 & \cdots & 0 \\
0 & \sqrt{s_{22}} & \cdots & 0 \\
\vdots  & \vdots  & \ddots & \vdots  \\
0 & 0 & \cdots & \sqrt{s_{pp}} 
\end{bmatrix}$$

$$\textbf{R} = \textbf{D}^{{-1}/{2}}\textbf{S}\textbf{D}^{{-1}/{2}}$$

## A demonstration of the package is shown below:
```{r setup}
# Loading the package
library(Lab1Intro)

# Loading the data from the file 'T1-2.DAT' to the data array 'data' 
data = read.delim("D:/MATH5793/Lab1Intro/T1-2.DAT",sep = "",header = FALSE)

# Finding the mean vector for the data array using the function mean_vector()
Lab1Intro::mean_vector(data)

# Finding the covariance matrix for the data array using the function covariance_matrix()
Lab1Intro::covariance_matrix(data)

# Finding the correlation matrix for the data array using the function correlation_matrix()
Lab1Intro::correlation_matrix(data)
```
#### Assessment for this course MATH 5793 is as follows:
1. Clicker quiz, each class and lab (Total 10%)
1. 4 assignments (Total 20%)
1. Laboratories (Total 10%)
1. 2 Mid-term exams (10% each, Total 20%)
1. 3 Projects (More weighting on third project, Total 10%) 
1. 1 Final exam (30%)
